---
title: "Friday Night Poker"
author: "Won Ha Gonzalez"
date: "7/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Friday Night Poker

Since Jeff has taken the time to put the spreadsheet together, I figured that I could use it to practice some things.  So, I decided to make some visualizations of our performances.

Updated as of Oct. 24th, 2020. 

I gave James editing privileges and he helped to automate the spreadsheet, so we shouldn't see anymore wild swings in player earnings. A new stat was also created to contextualize everyone's performance. It is in the spreadsheet; I called it wager efficiency here.

The big mover for side bets is James: +$115 since the MLB playoffs started and it turns out Mike is at the top of side bet performance.

Gabe has joined Abe in players to take down thanks to his back to back wins.

**Unresolved bets not included in calculations:**

1. Mike and Ubee's $100 side bet.  
+ Mike takes Patriots to win more games than Buccaneers.  Wash if NFL does not complete their season.
2. Mark and Mike's $500 side bet.
+ Mike takes Cam Newton to make the Hall of Fames.
3. John and Won Ha's $20 side bet.
+ John takes Albert Pujols to reach 700 Home Runs.
4. Mark and James's $100 side bet.
+ Mark takes Trump to win the election.
5. Mark and Won Ha's $50 side bet.
+ Mark takes Trump to win the election.

### Total Earnings Leaderboard

```{r Tot.Earn, echo=F}
Friday_Poker <- read.csv("C:/Users/wonha/Desktop/My Projects/Friday_Poker.csv")
Friday_Poker$Poker_Wagered <- Friday_Poker$Buy.ins*25
Friday_Poker$Poker_Earnings <- Friday_Poker$Poker_Winnings - Friday_Poker$Poker_Wagered 
Friday_Poker$Side_WinPct <- Friday_Poker$Side_Bets_Won/Friday_Poker$Side_Bets
Friday_Poker$Total_Action <- Friday_Poker$Buy.ins + Friday_Poker$Side_Bets
Friday_Poker$Total_Earnings <- Friday_Poker$Poker_Earnings + Friday_Poker$Side_Earnings
Friday_Poker$Wager_Efficiency <- round(Friday_Poker$Total_Earnings/Friday_Poker$Total_Action, 2)
Friday_Poker <- Friday_Poker[, c(1, 2, 8, 3, 4, 9, 5:7, 10:13)]

Total.Performance <- Friday_Poker[-c(14:18), c(1, 12, 13)]
Total.Performance[order(Total.Performance[,2], decreasing = TRUE),]
```

### Overall Winnings

```{r overall, echo=F, message=F, fig.height=7, fig.width=10}
##dealing with NaN for win pct.
Friday_Poker$Side_WinPct[is.na(Friday_Poker$Side_WinPct)] <- NA

## Create data set with active players
active.play <- Friday_Poker[which(Friday_Poker$Total_Action > 0), ]

library(ggplot2)
library(plotly)

p1 <- ggplot(active.play) + 
 aes(x = Total_Action, y = Total_Earnings, colour = Participants, size = Wager_Efficiency) +
 geom_point() + scale_color_hue() + 
 labs(x = "# of Bets", y = "Earnings ($)", title = "Friday Poker", subtitle = "Total Earnings vs. Total Bets Made", color = "Players", size = "Wager Efficiency") +
 theme_minimal()

ggplotly(p1)
```

### Poker Performance

```{r poker, echo=FALSE, fig.height=7, message=F, fig.width=10}
p2 <- ggplot(active.play) +
 aes(x = Buy.ins, y = Victories, colour = Participants, size = Poker_Winnings) +
 geom_point() +
 scale_color_hue() +
 labs(x = "# of Buy-Ins", y = "Games Won", title = "Friday Poker", subtitle = "Poker Results", color = "Players", size = "Money Earned") +
 theme_minimal()
ggplotly(p2)
```

### Side Bet Performance

```{r side, echo=F, message=F, fig.height=7, fig.width=11}
p3 <- ggplot(active.play) +
 aes(x = Side_Bets, y = Side_Earnings, colour = Participants, size = Side_WinPct) +
 geom_point() +
 scale_color_hue() +
 labs(x = "# of Side Bets", y = "Side Earnings ($)", title = "Friday Poker", subtitle = "Side Bets", color = "Players", size = "Win Pct.") +
 theme_minimal()
ggplotly(p3)
```



